---
title: "HRECOS: Data Management"
output: html_document
author: Zachary M. Smith
---

# Introduction

The goal of this section is to append HRECOS data provided by Stevens Insitute of Technology into a single CSV for each data type (raw and post).

Z. Smith requested and recieved HRECOS data from David Runnels (Stevens Institute of Technology) on 9/20/2018. The data was provided in two zipped folders ("raw_data" and "post_data") representing two data types (i.e., raw = unaltered data; post = processed/approved data). In each folder the files represent data for individual stations in a long data format. The files are stored as ".dat" but are CSVs.

# Setup

Import packages from the __tidyverse__ for data processing.
```{r}
suppressPackageStartupMessages(
  library(tidyverse)
)
```

Find the R-project root directory, which will be used to establish file paths in scripts below.
```{r}
root.dir <- rprojroot::find_root("trends.Rproj")
```

Establish a connection to the HRECOS PostgreSQL database. This connection will be used to write data to the database in subsequent scripts.
```{r}
con <- DBI::dbConnect(
  odbc::odbc(),
  driver = "PostgreSQL Unicode(x64)",
  database = "hrecos",
  UID = rstudioapi::askForPassword("Database user"),
  PWD = rstudioapi::askForPassword("Database password"),
  host = "localhost",
  port = 5432
  )
```

# Preprocess Data from Stevens Institute of Technology

This script loops through the "raw_data" and "post_data" folders, imports all of the ".dat" files, appends the files into a single data frame, and exports the data frame into the HRECOS PostgreSQL database.
```{r, results="hide", eval=process.stevens}
lapply(c("raw_data", "post_data"), function(dir.i) {
  file.vec <- list.files(
    file.path(root.dir,
              "data",
              "stevens_institute",
              dir.i)
  )
  
  import.df <- purrr::map_df(file.vec, function(file.i) {
    path.i <- file.path(root.dir,
                "data",
                "stevens_institute",
                dir.i,
                file.i)
    # print(file.i)
    size.i <- file.size(path.i)
    
    if (size.i > 0) {
      data.table::fread(
      path.i,
      col.names = c("station",
                    "parameter",
                    "date_time",
                    "value",
                    "flag",
                    "comment")
    ) %>% 
        mutate(date_time = as.POSIXct(date_time,
                                format = "%Y-%m-%d %H:%M:%S",
                                tz = "GMT"),
         date_time = format(date_time, 
                             tz = "EST"))
    }
    
  })
  
  # data.table::fwrite(import.df,
  #                    file.path(root.dir,
  #                              "data",
  #                              "cleaned",
  #                              paste0(dir.i, ".csv")))
  
   DBI::dbWriteTable(con, dir.i, import.df)
})
```

```{r}
DBI::dbWriteTable(con, "test", cars, 
                  field.types = list("text", "text"))

```

